---
title: "Correlation Null Hypothesis Significance Test"
author: "Amanda Mae Woodward"
date: "2022-11-30"
output: html_document
---
```{r}
library(readxl)
winterDat <- read_excel("~/Desktop/PSY4960-Fall2022/PSY4960- In Class Notes/PSY3801-Correlation example.xlsx")
```


# Research Question 
 
## More specific research question: Does enjoying outdoor winter activities have a positive relationship with liking winter?

### Step 1: Write out our hypotheses

#### Null Hypothesis: 
There is not a positive relationship between enjoying winter outdoor activities and liking winter 
r ≤ 0
#### Alternative hypothesis: 
There is a positive relationship between enjoying winter outdoor activities and liking winter
r>0

### Step 2: Choosing statistic 
correlation- we're interested in the linear relationship between these variables

### Step 3: Gather data; and set critical area

0.05; due to convention 
data collected from Google form in class 

### Step 4: Calculating Statistic
`cor.test()` gives u an associated p value with our correlation value
`cor.test(xvariable, y variable, alternative= "greater"/"less"/"two.sided")`
```{r}
cor.test(winterDat$`How much do you like winter? (1 = not at all; 15 = a lot!)`, winterDat$`how much do you like outdoor winter activities? (0 = staying by the fire inside ; 10= outside all winter!)`, alternative ="greater")
```

###Step 5: Draw a conclusion 
